\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-03-24 paper/gflp_model.tex
Update model.tex

Our interpretation of this model is that, while all units are prone to a mode of failure which can be approximated by a distribution with cdf $F_{d2}$, a proportion $\pi$ are {\em also} defective, and thus subject to another failure mode ($F_{d1}$).

@@

\begin{align*}
 \eta_{\sigma ,1} & \sim \op{Normal}(0, 0.5)\\
 \eta_{\sigma ,2} & \sim \op{Normal}(-0.75, .5)\\
 \tau_{\sigma ,1} & \sim \op{Gamma}(1, 2)\\
 \tau_{\sigma ,2} & \sim \op{Gamma}(1, 2)\\
 \eta_{t_{p_1},1} & \sim \op{Normal}(7, 1)\\
 \eta_{t_{p_2},2} & \sim \op{Normal}(9, 2)\\
 \tau_{t_{p_1},1} & \sim \op{Gamma}(1, 2)\\
 \tau_{t_{p_2},2} & \sim \op{Gamma}(1, 2)
 \end{align*}

>>>>

Our interpretation of this model is that,
\begin{enumerate}
\item All units of a given drive-model are exchangable
\item All units of drive-model $d$ have a primary failure mode
  which can be approximated by a distribution with cdf $F_{d2}$
\item A fraction of units of drive-model $d$, $\pi_d$, are defective,
  and thus subject to another failure mode. This failure mode can be
  approximated by a distribution, $F_{d1}$.
\end{enumerate}

@@

\begin{align*}
  \eta_{\pi} & \sim \op{Normal}(-3, 1)\\
  \tau_{\pi} & \sim \op{Cauchy}^+(0, 1)\\
  \eta_{\sigma ,2} & \sim \op{Normal}(0, 2)\\
  \tau_{\sigma ,2} & \sim \op{Cauchy}^+(0, 1)\\
  \eta_{t_{p_2},2} & \sim \op{Normal}(9, 2)\\
  \tau_{t_{p_2},2} & \sim \op{Cauchy}^+(0, 1)
 \end{align*}
